\MakeUppercase{Layered Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-23 k-planar.tex
Fixed theorem numbering

Here we discuss some of the consequences of Theorems~\ref{thm:1-planar}--\ref{thm:g-k-planar} for other graph parameters that can be bounded using layered partitions and other graph classes that are $k$-planar.

@@

Combining \lemref{non-repetitive} with Theorems~\ref{thm:1-planar}--\ref{thm:g-k-planar} we immediately obtain the following corollaries:

@@

Combining \lemref{p-centered} with Theorems~\ref{thm:1-planar}--\ref{thm:g-k-planar} immediately gives the following results, for every $p\ge 2$:

@@

We conclude by pointing out two other graph classes, namely $(g,d)$-map graphs and $(g,\delta)$-string graphs that are $(g,k)$-planar for $k=O(d^2)$ and $k=\delta^2$, respectively.  This implies that Theorems~\ref{thm:1-planar}--\ref{thm:g-k-planar} and Corollaries~\ref{cor:first}--\ref{cor:last} apply to $(g,d)$-map graphs and to $(g,\delta)$-string graphs.

>>>>

Here we discuss some of the consequences of Theorems~\ref{thm:k-planar}--\ref{thm:g-k-planar} for other graph parameters that can be bounded using layered partitions and other graph classes that are $k$-planar.

@@

Combining \lemref{non-repetitive} with Theorems~\ref{thm:k-planar}--\ref{thm:g-k-planar} we immediately obtain the following corollaries:

@@

Combining \lemref{p-centered} with Theorems~\ref{thm:k-planar}--\ref{thm:g-k-planar} immediately gives the following results, for every $p\ge 2$:

@@

We conclude by pointing out two other graph classes, namely $(g,d)$-map graphs and $(g,\delta)$-string graphs that are $(g,k)$-planar for $k=O(d^2)$ and $k=\delta^2$, respectively.  This implies that Theorems~\ref{thm:k-planar}--\ref{thm:g-k-planar} and Corollaries~\ref{cor:first}--\ref{cor:last} apply to $(g,d)$-map graphs and to $(g,\delta)$-string graphs.
